---
name: Conor M.
surname: Finlay
position: "Senior Research Fellow"
address: "Trinity Translational Medicine Institute, Trinity College Dublin"
phone: +353 857148825
profilepic: Conor.jpeg
#www: "github.com/Conorisco"
email: "cofinlay@tcd.ie; conor.finlay@manchester.ac.uk"
twitter: conorisco
github: conorisco
googlescholar: kQ6U7AkAAAAJ
#headcolor:
orcid: 0000-0001-8285-0903
#linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_md: true
    page_total: yes
#output: vitae::twentyseconds
aboutme: "Cellular Immunologist and bioinformatician combining molecular, in vivo and translational research. "
#docname: "Conor Finlay CV.pdf"
#headcolor: 	050583
fontsize: 10pt # be aware thea LaTeX has limitations and cannot make text less than 10pt
headcolor: 224190

---

<!-- # Career profile -->
<!-- I started my career in Trinity College Dublin identify pathways that shut down autoimmunity and allergy, leading to three papers in *The Journal of Immunology* and one in *Parasite immunology* and co-authorship in *Nature communications*. Next in Manchester I made a major advance on how adaptive immunity controls macrophages and how macrophage differentiation controls disease outcomes, publishing articles in *Immunity*, *elife*, *Nature Immunology* and *Parasite Immunology*. Recently, back in Ireland I have been conducting patient orientated research where I have submitted my first co-final author paper. I have received a best talk at the Irish Society of Immunology conference, been an invited speaker at 3 conferences and spoken at 13 more. I have received 8 awards. I have supervised 13 research students, reviewed articles, grants and will soon join *Frontiers in immunology* as a review editor. I am the member of 4 scientific societies, and sit on 3 committees. I am a co-inventor on a patent WM01-740-02 that has been commercialised as a biotech company Pravalix Tx.  -->

<!-- I am ready to educate the next generation of scientists and clinicians and lead my own group to make transformative discoveries. -->

<!-- #\fontsize{11}{18}{8}{8} -->
```{r install packages, include=FALSE}
#install.packages("tidyverse")
#install.packages("vitae")
#install.packages("rorcid")
#install.packages('scholar')
#install.packages("readxl")
#install.packages("knitr")
#install.packages('tinytex')
#install.packages("gridExtra")
#tinytex::install_tinytex() # installs LaTeX - some issues on windows (but only some)
# knitting for first time will take a while as it appears to install a bunch of tools for latex on run 1
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacs <- c('vitae','tidyverse','readr','readxl','rorcid','rmarkdown','knitr','scholar','cowplot','gridExtra','patchwork')
lapply(pacs, library, character.only=TRUE) #%>% invisible()
myor <- "0000-0001-8285-0903"
myscol <- 'kQ6U7AkAAAAJ'
col <- "#050583"
```

```{r google scholar, include=FALSE}
l <- get_profile(myscol)
p <- get_publications(myscol)
ct <- get_citation_history(myscol)
```

<!-- # Snapshot -->
<!-- My main research interest is in what genetic factors control mononuclear phagocyte (macrophage) differentiation during inflammation on a single cell level and how this impacts on disease outcomes. I have expertise in single cell RNA-sequencing, NGS, cell biology, *in vitro* and *in vivo* sciences and summarising complex data through effective data visualisation. -->
<!-- # SECTION 1 - applicant details -->

<!-- # Current roles -->


##  Senior Research Fellow, Trinity College Dublin (2022-present)

-   SFI-Pathways Programme Fellow (PI, starting August 2024)
-   TCD Omics - Single cell RNA-sequencing core service (founder and scientific director), since 2021 
-   HEALED consortium - molecular biology and sequencing lead (with Aideen Long), since August 2023
-   COVID-19 SFI-funded strategic partnership - transnational immunology ,up to mid-2023
-   Trinity Kidney Centre - lab management, student supervision(with Mark Little), up to mid-2023
-   Multi-modal clinical data analysis (with Mark Little), up to mid-2023
-   Co-supervising longitudinal immune cell phenotyping study, PARADISE project, (with Mark Little), 2022-present

## Honorary Research Fellow, University of Manchester (2021-present)

-   Collaboration on *MRC* programme grant with Prof. Judith Allen. 

# Past roles & Education
```{r}
emp <- read_excel("../data/employment_1_page.xlsx")
emp <- emp[-c(1:2),] # remove descriptive title
emp %>% arrange(desc(when)) %>% brief_entries(what =with , #subtitle
                                              when = when,
                                              with = where) #Rightmost)
```

<!-- # Education -->
<!-- ```{r} -->
<!-- edu <- read_excel("../data/education.xlsx")  -->
<!-- edu <- edu[-c(1:2),] # remove descriptive title -->
<!-- cols <- colnames(edu) -->
<!-- edu  %>% arrange(desc(when)) %>%  detailed_entries(what = what, #subtitle -->
<!--                          when = when, # to right -->
<!--                          why = why , # sub-subtitle -->
<!--                          with = with, # Major title -->
<!--                          where =  where) #Rightmost) -->

<!-- ``` -->

# Funding
I have received a total funding of 684,106 Euro in funding to my lab in Trinity. In the UK I co-wrote a programme grant (as Research Co-Investigator) on which I now collaborate.
<!-- ## Awarded -->
```{r}

gra <- read_excel("../data/grants.xlsx")
gra<- gra[-c(1:2),] # remove descriptive title
gra %>% arrange(desc(when))  %>% detailed_entries(what = what, #subtitle
                         when = when, # to right
                         why = why , # sub-subtitle
                         with = with, # Major title
                         where =  where) #Rightmost)

```

<!-- ## Funding - reserve list -->
<!-- <!-- --> 

<!--   **SFI Pathways program 2022**, €425,000. -->
<!--     -   *Macrophage Activation and Transition in the Autoimmune Kidney (MacATAK): uncovering functional outcomes of macrophage differentiation in the inflamed kidney*. -->
<!--     -   Scored 4.25/5 in international review and recommended for funding. Placed on SFI reserve list for funding until Q2 2024. -->

# Presentations, Awards & contributions

## Presentations

* [4 invited speaker presentations](https://github.com/Conorisco/CV/raw/main/CV_conorisco/CV_conorisco_AA2023.pdf)
* [13 conference oral presentations, selected from abstract ](https://github.com/Conorisco/CV/raw/main/CV_conorisco/CV_conorisco_AA2023.pdf), * [8 conference poster presentations](https://github.com/Conorisco/CV/raw/main/CV_conorisco/CV_conorisco_AA2023.pdf)   


## Awards and media

* [Commentry in *Immunity*: "Macrophages show up in style when Th2 lymphocytes organize their homecoming"](https://www.cell.com/immunity/fulltext/S1074-7613(23)00175-9)
* [Paper featured on The Immunology Podcast - Episode 51](https://www.immunologypodcast.com/ep-51-the-journey-of-cells-featuring-dr-doug-green)
* Immunity paper featured on August 2023 edition of *Journal of Allergy and Clinical Immunology* News Beyond Our Pages.

<!-- ## Oral Presentations -->

<!-- ```{r} -->
<!-- pres <- read_excel("../data/presentations.xlsx") -->
<!-- pres<- pres[-c(1:2),] # remove descriptive title -->
<!-- pres  %>% arrange(desc(when)) %>% filter(what != 'Poster presentation') %>% brief_entries( -->
<!--               what = with,# middle -->
<!--               when = when, -->
<!--               with = where) -->
<!-- ``` -->

<!-- ## Poster Presentations -->

<!-- ```{r} -->
<!-- pres <- read_excel("../data/presentations.xlsx") -->
<!-- pres<- pres[-c(1:2),] # remove descriptive title -->
<!-- pres  %>% arrange(desc(when)) %>% filter(what == 'Poster presentation') %>% brief_entries( -->
<!--               what = with,# middle -->
<!--               when = when, -->
<!--               with = where) -->
<!-- ``` -->



<!-- ## Awards -->

<!-- ```{r} -->
<!-- awards <- read_excel("../data/awards.xlsx") -->
<!-- awards<- awards[-c(1:2),] # remove descriptive title -->
<!-- awards %>% arrange(desc(when))  %>% brief_entries( -->
<!--               what = with ,# middle -->
<!--               when = when  # left -->
<!--     ) # right -->
<!-- ``` -->



<!-- ## Oral Presentations (details of 8X poster presentations availible in appendex) -->

```{r}
# pres <- read_excel("../data/presentations.xlsx")
# pres<- pres[-c(1:2),] # remove descriptive title
# pres  %>% arrange(desc(when)) %>% filter(what != 'Poster presentation') %>% brief_entries(
#               what = with,# middle
#               when = when,
#               with = where)
```

<!-- ## Awards -->

```{r}
# awards <- read_excel("../data/awards.xlsx")
# awards<- awards[-c(1:2),] # remove descriptive title
# awards %>% arrange(desc(when))  %>% brief_entries(
#               what = with ,# middle
#               when = when  # left
#     ) # right
```

## Discipline Contributions

* Reviewed articles for 6 journals. 
* Reviewed grants for 4 funding bodies
* Sat on 3 researcher interview panels
* Co-Inventor on a patent for Trinity Spin-out (Parvalis Tx)

<!-- ```{r} -->
<!-- rev <- read_excel("../data/reviewing.xlsx") -->
<!-- rev<- rev[-c(1:2),] # remove descriptive title -->
<!-- rev  %>% arrange(desc(when)) %>% brief_entries( -->
<!--               what = what,# middle -->
<!--               when = when, -->
<!--               with = with -->
<!--                 # left -->
<!--     ) # right -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #short version -->
<!--   sup <- read_excel("../data/collaborations_simple.xlsx") -->
<!-- sup<- sup[-c(1:2),] # remove descriptive title -->
<!-- sup  %>% arrange(desc(when)) %>% brief_entries( -->
<!--   #what = what, #subtitle -->
<!--                          #when = when, # to right -->
<!--                          what = with , # sub-subtitle -->
<!--                          with = where) # Major title) #Rightmost) -->

<!-- ``` -->
<!-- <!-- \newpage --> 

```{r}
# #long versions  
# sup <- read_excel("../data/collaborations.xlsx")
# sup<- sup[-c(1:2),] # remove descriptive title
# sup  %>% arrange(desc(when)) %>% detailed_entries(what = what, #subtitle
#                          when = when, # to right
#                          why = why , # sub-subtitle
#                          with = with, # Major title
#                          where =  where) #Rightmost)

```


<!-- # Teaching & Supervision -->

<!-- ## Formal teaching -->
<!-- ```{r} -->
<!-- #teaching short version  -->
<!-- # t <- read_excel("../data/teaching.xlsx") -->
<!-- # t<- t[-c(1:2),] # remove descriptive title -->
<!-- # t  %>% arrange(desc(when)) %>% brief_entries( -->
<!-- #               with= what ,# middle -->
<!-- #               when = when, -->
<!-- #               what = with# left -->
<!-- #     ) # right -->

<!-- t <- read_excel("../data/teaching.xlsx") -->



<!-- t %>% arrange(desc(when))  %>% detailed_entries(what = what, #subtitle -->
<!--                          when = when, # to right -->
<!--                          why = why , # sub-subtitle -->
<!--                          with = with, # Major title -->
<!--                          where =  where) #Rightmost) -->

<!-- ``` -->

```{r}
# #teaching long version 
# t <- read_excel("../data/teaching.xlsx")
# t<- t[-c(1:2),] # remove descriptive title
# t  %>% arrange(desc(when)) %>% brief_entries(
#               with= what ,# middle
#               when = when,
#               what = with# left
#     ) # right

```

# Research leadership and collaborations
```{r}
# for longer version of CV
# sup <- read_excel("../data/supervison.xlsx")
# sup<- sup[-c(1:2),] # remove descriptive title
# sup  %>% arrange(desc(when)) %>% detailed_entries(what = what, #subtitle
#                          when = when, # to right
#                          why = why , # sub-subtitle
#                          with = with, # Major title
#                          where =  where) #Rightmost)
```


**Student projects** 16 projects designed and supervised across Trinity (12-15 weeks) and Manchester (6 months). Currently co-suppervise a IRC-funded PhD student.

 **TCD Omics Core facility**. I have established formal pipelines for a single cell RNA-sequencing core service ‘TCD Omics’.
 
**16 active collaborations**, with groups in NIH, Leiden, Manchester, RCSI, Trinity college Dublin, St James' hospital.
 
<!-- \newpage -->

# Selected publications (last 3 years)
```{r}
library(dplyr)
#knitr::write_bib(c("vitae", "tibble"), "My collection.bib")

bibliography_entries("My Collection_3_year.bib") %>%
  arrange(desc(issued))

```
# Referee

[**Prof Judi Allen**](mailto:judi.allen@manchester.ac.uk ),	Professor of Immunobiology;	Lydia Becker Institute	University of Manchester

[Up to date long-form CV availible on GitHub (here)](https://github.com/Conorisco/CV/raw/main/CV_conorisco/CV_conorisco_AA2023.pdf) 