---
name: Conor M.
surname: Finlay
position: "Senior Research Fellow"
address: "Trinity Translational Medicines Insitute, Trinity College Dublin"
phone: +353 857148825
#www: "github.com/Conorisco"
email: "cofinlay@tcd.ie; conor.finlay@manchester.ac.uk"
twitter: conorisco
github: conorisco
orcid: 0000-0001-8285-0903
#linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Research interests 
I am a cellular Immunologist with three core skills: *in vivo* models of inflammation, bioinformatics and clinical research. My current research obsession is regulation of mononuclear phagocyte (macrophage/ denrtiic cells) differentiation during inflammation on a single cell level. 

# Roles
## Senior Research Fellow, Trinity College Dublin
 * COVID19 Strategic partnership
 * TCD Single cell Core development
 * Trinity Kidney Health Centre, Prof. Mark A Little.

## Honorary Research Fellow, University of Manchester
 * COVID19 Strategic partnership
 * TCD Single cell Core development
 * Trinity Kidney Health Centre, Prof. Mark A Little.


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
  "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
  "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

